A Large-scale Study of Polymorphism in R

### 2019-03-30 paper/main.tex
getting through L0

	\item \{double, integer\}: in R, doubles and integers are effectively interchangeable, as casting from one to the other is straightforward and automatically performed when appropriate.
	For example, \code{c(1, 2)[1.9] == 1}.
	We can easily consolidate these into one type, say a real number type.

@@

	\item \{X, NULL\}: in most languages, NULL is an inhabitant of all types, and we see that this is not the case in R.
	That said, there is a pattern of many functions having default or optional arguments, and in many of these cases NULL is the default value.
	This is a distinction that might be worth collapsing, and further this indicates that some annotation for optional arguments would be useful.

@@

>>>>

\begin{enumerate}

	\item \{double, integer\}: in R, doubles and integers are effectively interchangeable, as casting from one to the other is straightforward and automatically performed when appropriate.
	For example, \code{c(1, 2)[1.9] == 1}.

@@

	\item \{X, NULL\}: in most languages, NULL is an inhabitant of all types, and we see that this is not the case in R.
	That said, there is a pattern of many functions having default or optional arguments, and in many of these cases NULL is the default value.

@@

\end{enumerate}

How will we deal with this?

\begin{enumerate}

	\item consolidating doubles and integers into a single real-number type would account for all of this polymorphism.

	\item vectors!

	\item if we roll NULLs into every type, we can cleanly deal with these X, NULL signatures.
	As we have established that an annotation for an optional argument is useful, this will allow us to reveal other interesting patterns.

	\item similarly with NULLs, if we encounter a ...

	\item indices?

\end{enumerate}
